\section{Desert}
\begin{recipe}[source=Claire Saffitz]{Pecan Brittle Oatmeal Cookies}

\ingredients[15]{%
                 & \textbf{Pecan Brittle}\\
\unit[142]{g}    & Coarsely chopped pecans \\
\unit[150]{g}    & granulated sugar\\
\unit[57]{g}     & unsalted butter \\
\unit[1/2]{tsp}  & baking soda\\
\unit[1/2]{tsp}  & kosher salt\\
                 & \textbf{Cookies}\\
\unit[2]{sticks} & unsalted butter, cut into tbsp\\
\unit[173]{g}    & all-purpose flour\\
\unit[2]{tsp}    & kosher salt\\
\unit[1]{tsp}    & baking soda \\
\unit[200]{g}    & old-fashioned rolled oats\\
\unit[150]{g}    & dark brown sugar\\
\unit[100]{g}    & granulated sugar\\
\unit[2]{large}  & eggs (cold from the fridge)\\
\unit[1]{tbsp}   & vanilla extract\\
}

\preparation{% 
\\
\textit{Make the Pecan Brittle}
\step Preheat oven to 350 \faren. Coarsely chop the pecans and bake until fragrant 8-10 minutes. Do not burn nuts!
\step Combine salt and baking soda in a small container set near stove. Place silicon baking mat on baking sheet, set aside.
\step Combine sugar and butter in sauce pan over medium heat with ~2 tbsp of water. Stir until melted than switch to swirling the pan (this prevents crystal formation). 
\step Boil until the sugar/caramel reaches a deep golden. Turn off the heat and working quickly stir in the pecans. Finally add the  baking soda/salt mixture and stir until combined.
\step Pour the mixture onto the baking mat and flatten to a single layer while warm. Set aside too cool.
\step Once cool and solid break it into large chunks using your hands and then cut so the largest pieces are about the size of a pea (it doesn't have to be neat). Set aside.
\\
\textit{Make the batter}
\step Make brown butter from ONE of the sticks of butter (you are only browning half of the butter)
\step Pour the browned butter into the bowl of your stand mixer with the other stick of butter. This now needs to cool to room temperature.
\step Put the flour, baking soda, half of the oats, and half of the pecan brittle into the food processor and pulse until you have formed a flour. 
\step Add the brown and white sugar to the mixer and combine. Add the cold eggs one at a time and combine. Add the flour mixture and carefully combine.
\step Scoop 2 once (1/4 cup) blobs onto a baking sheet and refrigerate for 24 hours.
\step Preheat oven to 350 \faren. Place 6 dough balls on a lined baking sheet (they spread) and bake for 16-20 minutes rotating once after 12 minutes. 
}

\hint{
You can freeze the dough balls after they have been in the fridge for a delicious single cookie whenever you feel like turning on the oven!
}
\end{recipe}

\begin{recipe}[source = Laura Howerton]{Ginger Cookies}
\ingredients[15]{
\unit[4]{cups}   & All-purpose flour \\
\unit[2]{sticks} & unsalted butter \\
\unit[2]{tsp}    & baking soda \\
\unit[4]{tbsp}   & ground ginger \\
\unit[1]{tbsp}   & ground clove \\
\unit[1]{tbsp}   & nutmeg \\
\unit[2]{tbsp}   & cinnamon \\
2                & eggs\\
\unit[1/2]{cup}  & molasses \\
\unit[1]{cup}    & granulated sugar \\
\unit[1]{cup}    & brown sugar\\
}

\preparation{
\newline
\step Pre-heat oven to 350 \faren.
\step In a medium bowl stir together flour, ginger, baking soda, cinnamon, cloves, and salt; set aside.
\step In a large mixing bowl beat butter for 30 seconds, add the brown and white sugar, beat until combined. Beat in eggs and molasses until combined.
\step Add the dry ingredients to the wet ingredients.
\step Shape dough into 1-inch balls, place on cookie sheet and bake for 8 to 9 minutes until just done with the tops puffed. Cool on a wire rack.
}
\end{recipe}
\clearpage
\begin{recipe}[preparationtime= 2 hours 25 minutes, source = Meghan]
		{Baker's German Sweet Chocolate Cake}

		\ingredients[19]{
				                   & \textit{Cake}\\
				\unit[4]{oz}       & Baker's German's Sweet Chocolate \\
				\unit[1/2]{cup}    & water \\
				4                  & eggs, separated \\
				\unit[2]{cups}     & flour \\
				\unit[1]{tsp}      & baking soda \\
				\unit[1/4]{tsp}    & salt \\
				\unit[1]{cup}      & butter, softened \\
				\unit[2]{cups}     & sugar \\
				\unit[1]{tsp}      & vanilla \\
				\unit[1]{cup}      & buttermilk \\
							       & \textit{Coconut-Pecan Filling and Frosting}\\
				4                  & egg yolks \\
				\unit[1]{can}      & evaporated milk \\
				\unit[1 1/2]{cups} & sugar \\
				\unit[3/4]{cup}    & butter, cut into small pieces \\
				\unit[2 2/3]{cups} & Baker's Angel Flake Coconut \\
				\unit[1 1/2]{cups} & copped pecans \\
				\unit[1 1/2]{tsp}  & vanilla \\
		}
\preparation{\\
		\textit{Prepare the cakes}\\
		\step Heat oven to 350 \faren. Cover bottoms of 3 (9-inch) round pans with parchment; spray sides with cooking spray.
		\step Microwave chocolate and water in large bowl on high for 1 1/2 to 2 minutes or until chocolate is almost melted, stirring after 1 min. Stir until chocolate is completely melted.
		\step Beat egg whites in small bowl with mixer on high speed until stiff peaks form; set aside. Combine flour, baking soda and salt. Beat butter and sugar in large bowl with mixer until light and fluffy. Add egg yolks, 1 at a time, beating well after each. Blend in melted chocolate and vanilla. Add flour mixture alternating with buttermilk, beating until will blended after each addition.
		\step Add egg white; stir gently until well blended. Pour into prepared pans. 
		\step Bake 30 mins or until toothpick inserted in centers comes out clean. Immediately run small spatula around cakes in pans. Cool cakes in pans 15 mins. Remove from pans to wire racks; cool completely.\\
		\newline
		\textit{Make the Frosting}\\
		\step Whisk egg yolks and milk in large saucepan until blended.
		\step Add sugar and butter; cook, stirring constantly, over medium heat 12 min or until thickened and golden brown. Remove from heat.
		\step Add remaining ingredients; mix well. Cool to desired spreading consistency\\
		\newline
		\textit{Assemble the Cake}\\
		\step Spread frosting between cake layers and on top of cake.
}
\end{recipe}

\begin{recipe}[source = Epicurious]{Apple Cake with Caramel Topping}
		\ingredients[15]{
		                   & nonstick vegetable oil spray \\
		\unit[3]{cups}     & all-purpose flour \\
		\unit[2]{tsp}      & ground cinnamon \\
		\unit[1]{tsp}      & baking soda \\
		\unit[1]{tsp}      & salt \\
		\unit[1]{pound}    & Golden Delicious Apples \\
		\unit[2]{cups}     & packed brown sugar \\
		\unit[1 1/2]{cups} & vegetable oil \\
		\unit[1]{cup}      & sugar \\
		3                  & eggs \\
		\unit[4]{tsp}      & vanilla extract \\
		\unit[3/4]{cups}   & pecans coarsely chopped \\
		\unit[1/2]{cups}   & butter \\
		\unit[1/4]{cups}   & whole milk \\
		}

		\preparation{
		\step Preheat oven to 350 \faren. Spray 12-cup Bunt pan with nonstick spray. Sift flour, cinnamon, baking soda, and salt into medium bowl. Transfer 3 tbsp flour to Bunt pan and tilt to coat. Set pan aside.
		\step Peel, core, and cut apples into 1/3-inch cubes and place in a bowl with 2tbsp of the flour mixture, toss to coat apples.
		\step Combine 1 cup brown sugar, vegetable oil, 1 cup sugar, eggs, and 3 tbsp vanilla in a large bowl. Using electric mixer beat until mixture is thick. Gradually beat in remaining flour mixture. Fold apple mixture and pecans into batter; transfer to prepared Bunt pan.
		\step Bake cake until tester inserted near center comes out clean, about 1 hour. Transfer cake in pan to rack. Let stand while making caramel.
		\step Melt butter in heavy small skillet over medium hear. Whisk in remaining 1 cup brown sugar, then milk. Continue to whisk until topping is smooth and blended and comes to boil. Whisk in remaining 1 tsp vanilla. 
		\step Spoon 1/4 cup hot caramel topping over warm cake in pan. Let stand until topping is absorbed into cake about 15 minutes. Turn cake out onto platter. Pour remaining warm topping over cake. Let stand until cool.
		}

\end{recipe}
