\section{Gerlach Famous Recipes}

\begin{recipe}[source = Mom]{Butternut Squash Enchiladas}
		\ingredients[6]{
		1 & medium butter nut squash \\
		1/2 & medium yellow onion \\
		2-3 & cloves of garlic \\
		\unit[3-4]{cans} & Hatch-GREEN-enchilada sauce \\
		15-20 & good corn tortillas \\
			  & spoonful of cream cheese \\
			  & cheese for topping \\
		}

		\preparation{
		\step Preheat the oven to 420 \faren. Remove the top of the squash and cut it in half the long way. Remove the seeds, put the squash skin up in a Pyrex baking dish with ~ inch of water. Bake until very soft 40 minutes or so.
		\step Dice the onion and garlic and saute until soft in a pan.
		\step Scrape the squash out of the skin and combine in a large bowl with the cooked garlic and onions along with the cream cheese. Set aside.
		\step Preheat the oven to 350 \faren. Cover the bottom of a baking dish with enchilada sauce. Warm the tortillas. Place a tortilla in the sauce, fill, roll so the seam is down. Repeat until the dish is full. Cover in cheese. Bake until cheese and sauce are bubbling.
		\step Serve hot or store in the fridge or freezer.
		}
\end{recipe}

\begin{recipe}[source= Mom]{Spanish Rice}
		\ingredients[6]{
		2 & cloves of garlic \\
		\unit[1]{cup} & uncooked white rice \\
		\unit[1]{can} & fire roasted tomatoes \\
		1/2 & medium yellow onion \\
			& garlic powder \\
			& dried oregano \\
			& chilly powder \\
		}

		\preparation{
		\step Chop the onion and garlic, saute in a small amount of neutral oil until translucent. Add the dried rice. Toast for a couple of minutes until the rice begins to look cooked. 
		\step Add the spices to taste. Cook for 30 seconds to let the flavors come out. 
		\step Add the can of tomatoes and enough water to cover the rice. Cover and let simmer for 20 minutes. Do no open the lid.
		\step Once the rice has absorbed the water it is done. Fluff with a fork and serve or store in the fridge for up to 4 days.
		}
\end{recipe}
